---
title: "AMP"
output: html_document
date: "2024-04-29"
---

# Figure 1: Correlation between air pollutants and the incidence of lung cancer and breast cancer in the United Kingdom

```{r Figure_1, show_col_types = FALSE, echo=TRUE}

library(openair)
library(tidyverse)

uk_pollutants_all <- importAURN(site = "all", year = 2009:2019, data_type = "annual")

uk_pollutants_all <- uk_pollutants_all %>%
  mutate(year = lubridate::year(date))

uk_annual_average <- uk_pollutants_all %>%
  group_by(year) %>%
  summarise(
    avg_pm10 = mean(pm10, na.rm = TRUE),
    avg_pm25 = mean(pm2.5, na.rm = TRUE),
    avg_no = mean(no, na.rm = TRUE),
    avg_no2 = mean(no2, na.rm = TRUE),
    avg_nox = mean(nox, na.rm = TRUE),
    avg_o3 = mean(o3, na.rm = TRUE),
    avg_so2 = mean(so2, na.rm = TRUE)
  )

library(readr)

cancer_data <- read_csv("data/cancer_UK.csv")
cancer_data$Year <- as.integer(cancer_data$Year)
combined_data <- left_join(uk_annual_average, cancer_data, by = c("year" = "Year"))

library(dplyr)
library(ggplot2)
library(corrplot)  

cancer_pollutant_data <- combined_data %>%
  select(avg_pm10, avg_pm25, avg_no, avg_no2, avg_nox, avg_o3, avg_so2, lung_cancer, breast_cancer) 

cor_matrix <- cor(cancer_pollutant_data, use = "complete.obs") 

colors <- c(colorRampPalette(c("orange", "white"))(100), colorRampPalette(c("white", "red"))(100))

col_index <- function(cor_value) {
  round((cor_value + 1) * 99.5) + 1
}

png("correlation_matrix.png", width = 800, height = 600)

corrplot(cor_matrix, method = "circle",
         col = colors, 
         colorRampPalette = colors,  
         tl.col = "black",   
         tl.srt = 45,          
         tl.cex = 1.5,        
         cl.cex = 1,        
         addCoef.col = "white",  
         number.cex = 1.5)    

dev.off()

```

# Figure 2: Positive Correlation between 03 Levels and Breast Cancer Incidence

```{r Figure_2, show_col_types = FALSE, echo=TRUE}

ggplot(cancer_pollutant_data, aes(x = avg_o3, y = breast_cancer)) +
  geom_smooth(method = "lm", se = TRUE, color = "red", size = 1) +
  labs(title = "Positive Correlation between O3 Levels and Breast Cancer Incidence",
       x = "Average O3 Levels", y = "Breast Cancer Incidence") +
  theme_minimal() + 
  theme(
    plot.title = element_text(size = 20, face = "bold"),  
    axis.title = element_text(size = 16),  
    axis.text = element_text(size = 14) 
  ) +
  geom_path(aes(x = 42, y = 14000), arrow = arrow(length = unit(0.5, "cm")), color = "black") +
  geom_path(aes(x = 50, y = 14000), arrow = arrow(length = unit(0.5, "cm")), color = "black")

ggsave("breast_cancer_o3_relationship.png", 
       plot = ggplot(cancer_pollutant_data, aes(x = avg_o3, y = breast_cancer)) +
              geom_smooth(method = "lm", se = TRUE, color = "red", size = 1) + 
              labs(title = "Positive Correlation between O3 Levels and Breast Cancer Incidence",
                   x = "Average O3 Levels", y = "Breast Cancer Incidence") +
              theme_minimal() +
         theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 16), 
    axis.text = element_text(size = 14) 
  ),  
       width = 10, height = 8, dpi = 300)

```

# Figure 3: Positive Correlation between 03 Levels and Lung Cancer Incidence

```{r Figure_3, show_col_types = FALSE, echo=TRUE}
ggplot(cancer_pollutant_data, aes(x = avg_o3, y = lung_cancer)) +
  geom_smooth(method = "lm", se = TRUE, color = "red", size = 1) + 
  labs(title = "Positive Correlation between O3 Levels and Lung Cancer Incidence",
       x = "Average O3 Levels", y = "Lung Cancer Incidence") +
  theme_minimal()  

ggsave("lung_cancer_o3_relationship.png", 
       plot = ggplot(cancer_pollutant_data, aes(x = avg_o3, y = lung_cancer)) +
              geom_smooth(method = "lm", se = TRUE, color = "red", size = 1) + 
              labs(title = "Positive Correlation between O3 Levels and Lung Cancer Incidence",
                   x = "Average O3 Levels", y = "Lung Cancer Incidence") +
              theme_minimal() + 
         theme(
    plot.title = element_text(size = 20, face = "bold"),  
    axis.title = element_text(size = 18), 
    axis.text = element_text(size = 18) 
  ),  
       width = 10, height = 8, dpi = 300)

```

# Figure 4: Results of regression analyses of air pollutants and lung, breast cancer incidence rates

```{r Figure_4, show_col_types = FALSE, echo=TRUE}

lung_o3_model <- lm(lung_cancer ~ avg_o3, data = cancer_pollutant_data)
summary(lung_o3_model)
confint(lung_o3_model)

breast_o3_model <- lm(breast_cancer ~ avg_o3, data = cancer_pollutant_data)
summary(breast_o3_model)
confint(breast_o3_model)

```

# Figure 5: Scatter chart of PM2.5 concentration and population Density in 2019 (by city)

```{r Figure_5, show_col_types = FALSE, echo=TRUE}

library(ggplot2)
library(dplyr)


PM2_5_Population_data <- read_csv("data/PM2.5_map_data.csv")  

PM2_5_Population_data$FactValueNumeric <- as.numeric(PM2_5_Population_data $FactValueNumeric)
PM2_5_Population_data$Population_density <- as.numeric(PM2_5_Population_data $Population_density)

ggplot(PM2_5_Population_data, aes(x=Population_density, y=FactValueNumeric, label=Location, color=ParentLocationCode)) +
  geom_point() + 
  geom_text(aes(label=Location), vjust=-1, hjust=0.5) + 
  labs(title="PM2.5 vs. Population Density by Region (2019)",
       x="Population Density (per sq km)", 
       y="Annual average pm2.5 emissions (µg/m3)") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, face = "bold"), 
    axis.title = element_text(size = 14), 
    axis.line = element_line(color = "black", size = 0.5) 
  ) +
  scale_color_manual(values=c("Asia"="blue", "Africa"="red", "Australia"="green", "Europe"="purple", "North America"="orange", "South America"="yellow"),
                     labels=c("Asia", "Africa", "Australia", "Europe", "North America", "South America")) 

ggsave("PM25_vs_PopDensity.png", width = 10, height = 8, dpi = 300)

```

# Figure 6: Positive Correlation between population density and PM2.5 concentration in 2019

```{r Figure_6, show_col_types = FALSE, echo=TRUE}

ggplot(PM2_5_Population_data, aes(x = Population_density, y = FactValueNumeric)) +
  geom_smooth(method = "lm", se = TRUE, color = "red", size = 1) + 
  labs(title = "Positive Correlation between population density and average annual PM2.5 concentration",
       x = "Population Density (per sq km)", y = "Average Annual PM2.5 Concentration (µg/m3)") +
  theme_minimal() 

ggsave("regression_plot.png", 
       ggplot(PM2_5_Population_data, aes(x = Population_density, y = FactValueNumeric)) +
  geom_smooth(method = "lm", se = TRUE, color = "red", size = 1) + 
  labs(title = "Positive Correlation between population density and PM2.5 concentration",
       x = "Population Density (per sq km)", y = "Average Annual PM2.5 Concentration (µg/m3)") +
  theme_minimal() + 
         theme(
    plot.title = element_text(size = 17, face = "bold"), 
    axis.title = element_text(size = 18),
    axis.text = element_text(size = 18) 
  ), 
       width = 10, height = 8, dpi = 300)

```

# Figure 7: Results of regression analyse of population density and PM2.5 concentration in 2019

```{r Figure_7, show_col_types = FALSE, echo=TRUE}

Population_model <- lm(Population_density ~ FactValueNumeric, data = PM2_5_Population_data)
summary(Population_model)

```

# Figure 8.1: PM2.5 Concentration Map of London (2019)

```{r Figure_8.1, show_col_types = FALSE, echo=TRUE}
library(ggplot2)
library(sf)
library(readr)

london_shapefile <- st_read("/Users/yangyuehan/Downloads/London-wards-2018/London-wards-2018_ESRI")

london_population <- read_csv("data/london_population.csv")
london_population_sf <- st_as_sf(london_population, coords = c("Longitude", "Latitude"), crs = 4326)
london_population_sf <- st_transform(london_population_sf, crs = st_crs(london_shapefile))
london_population_sf$PM2.5 <- as.numeric(london_population_sf$PM2.5)
london_map <- st_join(london_shapefile, london_population_sf, join = st_nearest_feature)


ggplot(london_map) +
  geom_sf(aes(fill = PM2.5)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", name = "PM2.5 Concentration") +
  theme_minimal() +
  theme(plot.title = element_text(size = 20, face = "bold")) + 
  labs(title = "PM2.5 Concentration Map of London")


ggsave("london_PM2.5_map.png", width = 10, height = 8, dpi = 300)


```

# Figure 8.2: Population Density Map of London (2019)

```{r Figure_8.2, show_col_types = FALSE, echo=TRUE}

ggplot(london_map) +
  geom_sf(aes(fill = Population_per_square_kilometre)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", name = "Population Density") +
  theme_minimal() +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  labs(title = "Population Density Map of London")

ggsave("london_population_map.png", width = 10, height = 8, dpi = 300)

```

# Figure 9: PM2.5 exposure in London versus other cities (2000-2019)

```{r Figure_9, show_col_types = FALSE, echo=TRUE}

library(readr)
London_comparision <- read_csv("data/London_comparision.csv")
ggplot(London_comparision, aes(x=City, y=Exposure_Mean, fill=City)) +
  geom_violin(trim=FALSE) + 
  geom_boxplot(width=0.1, fill="white") + 
  labs(title="PM2.5 exposure in London versus other cities (2000-2019)", x="City", y=" PM2.5 (µg/m3)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(plot.title = element_text(size = 20, face = "bold"))
ggsave("London_comparision.png", width = 10, height = 8, dpi = 300)

stats <- London_comparision %>%
  group_by(City) %>%
  summarise(
    Min = min(Exposure_Mean, na.rm = TRUE),
    Q1 = quantile(Exposure_Mean, 0.25, na.rm = TRUE),
    Median = median(Exposure_Mean, na.rm = TRUE),
    Q3 = quantile(Exposure_Mean, 0.75, na.rm = TRUE),
    Max = max(Exposure_Mean, na.rm = TRUE)
  )

print(stats)

```

# Figure 10: Box plot results

```{r Figure_10, show_col_types = FALSE, echo=TRUE}

library(readr)
London_global_comparision <- read_csv("data/London_global_comparision.csv")
London_global_comparision$Year <- as.Date(as.character(London_global_comparision$Year), format="%Y")

ggplot(London_global_comparision, aes(x=Year)) +
  geom_line(aes(y=`London, United Kingdom`, colour="London, United Kingdom"), size=1) +
  geom_line(aes(y=Global, colour="Global"), size=1) +
  geom_line(aes(y=`United Kingdom`, colour="United Kingdom"), size=1) +
  geom_hline(aes(yintercept=AQG, linetype="AQG"), size=1, colour="green") +
  scale_color_manual(values=c("London, United Kingdom"="green", "Global"="yellow", "United Kingdom"="red", "AQG"="blue")) +
  labs(title="Average Annual Population-Weighted PM2.5",
       x="Year", y="Annual population Weighted PM2.5 (µg/m3)") +
  theme_minimal() +
  theme(legend.title=element_blank())


```








